The pollination trade-off

### 2018-10-18 paper/manuscript.Rmd
remove extra space in awknoledgements
Add Jason's funding
Close #29
list changes to the manuscript

@@

We thank  Cátedra de Botánica General, Facultad de Agronomía, Universidad de Buenos Aires. 
The Agrasar and Bordeu families, and the University of Buenos Aires, for logistical support and permission to conduct this study at estancias Anquilóo, Las Chilcas and San Claudio, respectively.  
Field work was supported by grants PICT 08–12504 and 0851. 
EFC acknowledges the support from the University of Canterbury Doctoral Scholarship, the University of Canterbury Meadow Mushrooms Postgraduate Scholarship, and a New Zealand International Doctoral Research Scholarship.
DBS acknowledges the support of a Marsden Fast-Start grant and a Rutherford Discovery Fellowship, administered by the Royal Society Te Aparangi.

>>>>

### Changes

* Use AICc instead of AIC (no change in results)
* To keep signature of phenology, absolute flower counts (log-transformed) are used instead of relative abundances
* Columns in the trait matrix for phenology are scaled so that it doesn't count 5 times as much as other traits
* Boostraping resampling worked

@@

We thank  Cátedra de Botánica General, Facultad de Agronomía, Universidad de Buenos Aires. 
The Agrasar and Bordeu families, and the University of Buenos Aires, for logistical support and permission to conduct this study at estancias Anquilóo, Las Chilcas and San Claudio, respectively. 
Field work was supported by grants PICT 08–12504 and 0851. 
EFC acknowledges the support from the University of Canterbury Doctoral Scholarship, the University of Canterbury Meadow Mushrooms Postgraduate Scholarship, and a New Zealand International Doctoral Research Scholarship.
DBS and JMT acknowledge the support of a Rutherford Discovery Fellowship. 
DBS also awknoledges the Marsden Fund Council from New Zealand Government funding.
